---
title: "Milestone_5"
author: "Charles James"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Milestone_5"
author: "Charles James"
date: "`r Sys.Date()`"
output: pdf_document
---



```{r}
titanic = read.csv("titanic.csv")
colnames(titanic)
dim(titanic)

age = titanic$Age
```

# Age Analysis
```{r}
age_mean <- mean(age, na.rm=TRUE)
age_mean
age_median <- median(age, na.rm=TRUE)
age_median
age_variance <- var(age, na.rm=TRUE)
age_variance
age_sd <- sd(age, na.rm=TRUE)
age_sd
```
The Age histogram mostly resembles the normal distribution with minor skewing 
to the right. These large outlier ages will bring the mean slightly higher 
than the median. The mean age is 29.7 while the median age is 28 becuase of the 
minor outliers. The standard deviation of 14 means that the majority of people 
on board were between the age of 16 - 44 since the mean is approximately 30. 
This shows that the age values are spread out from one another.


# Fare Analysis
```{r}
fare = titanic$Fare
fare_mean = mean(fare)
fare_mean
fare_median = median(fare)
fare_median
fare_variance = var(fare)
fare_variance
fare_sd = sd(fare)
fare_sd
```


The fare data is also skewed right like the age histogram. Here though the 
outlier fares are significantly larger than the rest of the data. This is why
the mean is more than two times the median. The standard deviation of 49 when
the mean is 32 is really high and suggests that the data is heavily spread out.
Alot of this is cause by the one trip over $500.

###

