---
title: "Milestone_8"
author: "Charles James"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
titanic = read.csv("titanic.csv")
```

```{r}
contingency_table <- table(titanic$Sex, titanic$Survived)
print(contingency_table)
result <- prop.test(contingency_table)
print(result)
```
The P-value for the proportion testing is very low. 
P = 2.2e-16

Given this P-value we must reject the null hypothesis that the proportions of female survivors is equal to the proportion of male survivors. 
Female passengers had a statistically significant higher chance of survival. 




Test 2:


```{r}

survived_age <- titanic$Age[titanic$Survived == 1]
non_survived_age <- titanic$Age[titanic$Survived == 0]


t_test_result <- t.test(survived_age, non_survived_age)
t_test_result
```
With a P-value of .04119 we reject the null hypothesis that the true difference in means are equal to 0. 
The alternatice hypothesis is supported, which states that the true difference in means are not equal to 0. 
The mean of the ages are suvivors are lower than does who did not survive.



